Twists of supersymmetric gauge theories

### 2019-07-19 paper.tex
BRST

>>>>

\begin{dfn}
A {\bf classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item a $\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
\item a differential operator
\[
Q_{BRST} : \cF \to \cF^!  ;
\]
\item a local functional $I_{BRST} \in \oloc^+(\cF)$ of polynomial degree $\geq 3$.
\end{itemize}
Together, this data must satisfy the master equation
\[
[\d_{CE}, Q_{BRST}] + \d_{CE} I_{BRST} = 0 .
\]
\brian{even separately, I suppose?}
\end{dfn}

One can think of the space of field $\cF$ as a (linear) graded manifold.
In doing so, the $L_\infty$ structure on $\cF[-1]$ determines a vector field $X$ of cohomological degree $+1$ on this graded manifold. 
The operator $Q$ determines a one-form on $\cF$, and the master equation says that this one-form vanish along the vector field $X$. 
Similarly, the condition $\d_{CE} I = 0$ means the function $I$ on $\cF$ vanish along $X$.

From a classical BRST theory $(\cF, Q_{BRST}, I_{BRST})$, one can construct a classical BV theory as follows. 
Let $\{\ell_k\}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.

First, we define the free BV theory. 
This will only use the linear operation on the $L_\infty$ algebra $\cF$, and the operator $Q_{BRST}$. 
The underlying bundle of the BV theory is
\[
E = F \oplus F^! [-1] = F \oplus F^* \otimes {\rm Dens}_M .
\]
The differential of the free BV theory is
\[
Q = \ell_1 + Q_{BRST} .
\]
The BV pairing is defined by the composition
\[
E \otimes E = (F \oplus F^![-1]) \otimes (F \oplus F^![-1]) \to F \otimes F^! [-1] \oplus F^![-1] \otimes F \to {\rm Dens}_M [-1] .
\]
In the first arrow, we have used the obvious projection. 
The second arrow is given by the evaluation pairing between $F$ and $F^*$. 
The data $(\cE, Q, \omega)$ defines a free BV theory.

The interacting theory is constructed as follows.
First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p : \cE = \cF \oplus \cF^![-1] \to \cF$. 
These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
\[
I_{F} (e) = \sum_{k \geq 2} \int_M \frac{1}{(k+1)!} \omega(e, (p^*\ell_k) (e, \ldots, e)) . 
\] 
Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
\[
I_{BV} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
\]

\begin{lemma}
Given a classical BRST theory $(F, Q_{BRST}, I_{BRST})$, the data $(E, Q, \omega, I) = (F \oplus F^![-1] , \ell_1 + Q_{BRST} , I_{BV})$ defines a classical BV theory.
That is, the BV classical master equation
\[
Q I + \frac{1}{2} \{I, I\} = 0 \iff (Q + \ell_1) (I_F + p^*I_{BRST}) + \frac{1}{2} \{I_F + p^*I_{BRST}, I_F + p^*I_{BRST}\} = 0
\]
holds.
We refer to this classical BV theory as the {\bf $(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
\end{lemma}
